Which ITG Stepcharts are Turniest?

### 2016-03-14 itg/paper.tex
Fix step author turniness table; add related work section; fix other stuff

Of course, composing a stepchart of nothing but the theoretically-turniest patterns would be extremely tiresome (in more ways than one).
We turn our attention to existing ITG charts which were developed prior to this study, to investigate how much ITG players turn in the real world.
We processed every stepchart in our collection, which includes 70+ song packs.
Most well-known pack series from the ITG community are included, such as {\em Cirque}, {\em ITG}, {\em Mute Sims}, {\em Pendulum}, {\em r21*}, {\em SPEEDCOOOORE}, {\em The Legend of Zim}, and {\em Valex's Magical 4-Arrow Adventure}.

@@

\begin{table}[t]
	\begin{center}
		\small
	\begin{tabular}{l|c|c}
		Song Pack & \# of Charts & Avg. $\mathcal{T}$ \\
		\hline
		Valex's Magical 4-Arrow Adventure 5 & 150 & 0.964 \\
		Valex's Magical 4-Arrow Adventure 4 & 170 & 0.956 \\
		Valex's Magical 4-Arrow Adventure 3 & 155 & 0.950 \\
		Valex's Magical 4-Arrow Adventure 7 & 150 & 0.937 \\
		Valex's Magical 4-Arrow Adventure 2 & 130 & 0.929 \\
		Valex's Magical 4-Arrow Adventure   & 95 & 0.919 \\
		Valex's Magical 4-Arrow Adventure 6 & 145 & 0.917 \\
		Subluminal & 16 & 0.906 \\
		The Legend of Zim 1 & 26 & 0.906 \\
		FoxyMix 5 & 30 & 0.901 \\
		FoxyMix 4 - Nuclear Overdrive & 68 & 0.899 \\ 
		Mute Sims 9 & 48 & 0.886 \\
		In The Groove Rebirth + & 147 & 0.881 \\
		StepMania 5 & 5 & 0.869 \\
		\multicolumn{3}{c}{\normalsize\dots} \\
		Stephcharts and Richarts & 81 & 0.770 \\
		Tachyon Delta & 32 & 0.769 \\
		Tachyon Alpha & 151 & 0.769 \\
		Sexuality Violation 2 & 219 & 0.766 \\
		TLOES Chapter 1 & 120 & 0.765 \\
		Fort Rapids V (12s-16s) r3 Final & 98 & 0.759 \\
		Noisiastreamz & 20 & 0.758 \\
		In The Groove & 331 & 0.754 \\
		Pendulum & 150 & 0.747 \\
		SPEEDCOOOORE 2 & 70 & 0.731 \\
		SPEEDCOOOORE & 47 & 0.709 \\
		The Legend of Zim 3 & 40 & 0.702 \\
		The Legend of Zim 4 & 44 & 0.701 \\
		The Legend of Zim 5 & 19 & 0.667 \\
	\end{tabular}
	\end{center}
	\caption{The turniest and least turny stepfile packs. Wow, great job Valex! Zim had a good thing going but has been slacking off recently.}
	\label{tab:pack}
\end{table}
\begin{table}[t]
	\begin{center}
		\small
	\begin{tabular}{l|c|c}
		Step Artist & \# of Charts & Avg. $\mathcal{T}$ \\
		\hline
		M. Emirzian & 25 & 0.981 \\
		sssmsm & 40 & 0.980 \\
		M. Calfin & 16 & 0.947 \\
		J. Berkowitz (Valex) & 1016 & 0.940 \\
		B. Dinh & 10 & 0.919 \\
		J. DeGarmo & 24 & 0.915 \\
		X. Ythar & 17 & 0.914 \\
		R. McKanna & 59 & 0.895 \\
		R. Woods & 18 & 0.892 \\
		Fraxtil & 23 & 0.880 \\
		\multicolumn{3}{c}{\normalsize\dots} \\
		I. Pyles & 175 & 0.754 \\
		P. Shanklin & 29 & 0.752 \\
		Gazebo & 355 & 0.751 \\
		zimlord & 199 & 0.750 \\
		C. Emirzian & 17 & 0.736 \\
		Mootz & 22 & 0.734 \\
		B. Abear & 27 & 0.729 \\
		Insane Steve & 41 & 0.718 \\
		Blazing & 15 & 0.696 \\
		C. Foy & 138 & 0.678 \\
	\end{tabular}
	\end{center}
	\caption{The turniest and least turny step authors. Only authors with 10 or more charts are included.}
	\label{tab:artist}
\end{table}
Beyond these extreme examples, we are interested in some more normal charts people might actually like to play.
Table~\ref{tab:feets} shows the turniest charts of each level, for the most popular difficulty levels ranging from 7 to 17.
So, next time you want to work on your laterals or candles, you have me to thank!

@@

\defcitealias{ode}{Anonymized 2016}
{\bf Jumps.} The most obvious next step for this work is to account for jumps.
This seems quite easy: compute the two possible facings of the jump, depending which foot lands on which arrow, and use whichever facing produces the least turniness when compared to the previous and next steps in the sequence.
Honestly, we should have implemented that for this paper, but we only realized how it should work after we finished computing our dataset;
and owing to an inferior conference's deadline coming up in 10 days \citepalias{ode}, we don't have time for re-running experiments \citepalias{ode}.

@@

{\bf Fractional Turns.}
Experienced ITG players do not step with their feet on the middle of each arrow; rather, they try to step on the edges and ``brackets'' between arrows, hitting each step with heel or toes only to minimize the distance their feet must move.
This tendency distinguishes further granularity of turning than what we identify in this work.
Consider the two streams shown in Figure~\ref{fig:future} (a) and (b).
Although they measure the same $\mathcal{T}$ value of $1$,
(b) is considerably more exhausting to step, as (a) allows the player to bracket the entire run.
Future work could handle this by counting a 1-turn step as the full value only if the player subsequently continues turning farther in the same direction (which would force the player's feet off the brackets), and otherwise assign $\mathcal{T}=1/2$ for such a step.

@@

Following are the most turny 18-step patterns that are totally vanilla, with turniness of 1.375. (Manual inspection reveals the true turniness to be 4/3.)

@@

Following are the most turny 18-step patterns that may include crossovers only, with turniness of 1.5.

@@

Following are the most turny 18-step patterns that may include crossovers and laterals, with turniness of 1.625. (Manual inspection reveals the true turniness to be 8/5.)

@@

Following are the most turny 18-step patterns that may include crossovers, laterals, and 270s, with turniness of 1.625.
(Manual inspection reveals irregularity; these streams exhibit no core pattern that can be repeated to retain the maximum turniness.)

@@

Following are the most turny 18-step patterns that may include any pattern, with turniness of 2.

@@

\bibliographystyle{abbrvnat}
\bibliography{citations}

>>>>

Of course, composing a stepchart of nothing but the theoretically-turniest patterns would be extremely tiresome (in more ways than one).
We turn our attention to existing ITG charts which were developed prior to this study, to investigate how much ITG players turn in the real world.
We processed every stepchart in our collection, which includes 70+ song packs.
Most well-known pack series from the ITG community are included, such as {\em Cirque}, {\em ITG}, {\em Mute Sims}, {\em Pendulum}, {\em r21*}, {\em SPEEDCOOOORE}, {\em The Legend of Zim}, {\em Valex's Magical 4-Arrow Adventure}, and {\em Oh Henry! Mad Stamina: Streamy $\cdot$ Brutal $\cdot$ Stamina Bar in Milk Chocolate}.

@@

\begin{table}[t]
	\begin{center}
		\small
	\begin{tabular}{l|c|c}
		Song Pack & \# of Charts & Avg. $\mathcal{T}$ \\
		\hline
		Valex's Magical 4-Arrow Adventure 5 & 150 & 0.964 \\
		Valex's Magical 4-Arrow Adventure 4 & 170 & 0.956 \\
		Valex's Magical 4-Arrow Adventure 3 & 155 & 0.950 \\
		Valex's Magical 4-Arrow Adventure 7 & 150 & 0.937 \\
		Valex's Magical 4-Arrow Adventure 2 & 130 & 0.929 \\
		Valex's Magical 4-Arrow Adventure   & 95 & 0.919 \\
		Valex's Magical 4-Arrow Adventure 6 & 145 & 0.917 \\
		Subluminal & 16 & 0.906 \\
		The Legend of Zim 1 & 26 & 0.906 \\
		FoxyMix 5 & 30 & 0.901 \\
		FoxyMix 4 - Nuclear Overdrive & 68 & 0.899 \\ 
		Mute Sims 9 & 48 & 0.886 \\
		In The Groove Rebirth + & 147 & 0.881 \\
		StepMania 5 & 5 & 0.869 \\
		Cirque du Zeppelin & 109 & 0.867 \\
		In The Groove 3 & 448 & 0.858 \\
		\multicolumn{3}{c}{\normalsize\dots} \\
		Piece of Cake 5 & 20 & 0.785 \\
		Cirque du Veyron & 30 & 0.777 \\
		Stephcharts and Richarts & 81 & 0.770 \\
		Tachyon Delta & 32 & 0.769 \\
		Tachyon Alpha & 151 & 0.769 \\
		Sexuality Violation 2 & 219 & 0.766 \\
		TLOES Chapter 1 & 120 & 0.765 \\
		Fort Rapids V (12s-16s) r3 Final & 98 & 0.759 \\
		Noisiastreamz & 20 & 0.758 \\
		In The Groove & 331 & 0.754 \\
		Pendulum & 150 & 0.747 \\
		SPEEDCOOOORE 2 & 70 & 0.731 \\
		SPEEDCOOOORE & 47 & 0.709 \\
		The Legend of Zim 3 & 40 & 0.702 \\
		The Legend of Zim 4 & 44 & 0.701 \\
		The Legend of Zim 5 & 19 & 0.667 \\
	\end{tabular}
	\end{center}
	\caption{The turniest and least turny stepfile packs. Wow, great job Valex! Zim had a good thing going but has been slacking off recently.}
	\label{tab:pack}
\end{table}
\begin{table}[t]
	\begin{center}
		\small
	\begin{tabular}{l|c|c}
		Step Artist & \# of Charts & Avg. $\mathcal{T}$ \\
		\hline
		M. Emirzian	& 38	& 0.992 \\
		sssmsm		& 50	& 0.945 \\
		J.Berkowitz (Valex)	& 1025	& 0.939 \\
		B. Dinh		& 10	& 0.919 \\
		J. DeGarmo	& 26	& 0.906 \\
		J. Frederick	& 176	& 0.881 \\
		Fraxtil		& 23	& 0.880 \\
		M. Calfin	& 26	& 0.880 \\
		X. Ythar	& 24	& 0.879 \\
		R. Woods	& 22	& 0.874 \\
		R. McKanna	& 76	& 0.872 \\
		MIDI		& 86	& 0.870 \\
		Dark Luke	& 36	& 0.866 \\
		@@		& 60	& 0.859 \\
		D. Bernardone	& 354	& 0.858 \\
		D. D'Amato	& 154	& 0.857 \\
		\multicolumn{3}{c}{\normalsize\dots} \\
		%Konami	& 817	& 0.854 \\
		%NEMORIGINAL	& 63	& 0.85 \\
		%D. Renzetti	& 26	& 0.846 \\
		%D. Runberg	& 66	& 0.844 \\
		%Zaia	& 322	& 0.842 \\
		%Blank	& 272	& 0.841 \\
		%Driving55	& 21	& 0.833 \\
		%JOE2	& 16	& 0.83 \\
		%Wastum	& 19	& 0.83 \\
		%mute	& 410	& 0.828 \\
		%MacGravel	& 55	& 0.827 \\
		%T. Swag	& 13	& 0.826 \\
		%NIQ9	& 29	& 0.825 \\
		%C. Emirzian	& 27	& 0.823 \\
		%t0ni	& 75	& 0.821 \\
		%R. Uchima	& 122	& 0.819 \\
		%BlueChaos	& 104	& 0.818 \\
		%Brendino	& 14	& 0.816 \\
		%T. Moore	& 66	& 0.813 \\
		%Aoreo	& 216	& 0.813 \\
		%mudkyp	& 35	& 0.811 \\
		%King of Light	& 39	& 0.809 \\
		%G. Marchan	& 18	& 0.806 \\
		%Mad Matt	& 383	& 0.806 \\
		%Arvin	& 64	& 0.806 \\
		%Sudzi781	& 99	& 0.803 \\
		%S. Venkat	& 82	& 0.803 \\
		%Kindan	& 17	& 0.801 \\
		%Renard	& 53	& 0.799 \\
		%J. Nero	& 194	& 0.796 \\
		%W. Hodge	& 51	& 0.795 \\
		%Jayce	& 43	& 0.79 \\
		%WinDEU	& 49	& 0.787 \\
		M. Simmons	& 334	& 0.787 \\
		Revolver	& 25	& 0.775 \\
		R. Konkul (Rynker)	& 125	& 0.774 \\
		K. Ward	(\smiley) & 600	& 0.773 \\
		Freyja		& 89	& 0.766 \\
		P. Mason	& 14	& 0.765 \\
		M. Puls		& 167	& 0.759 \\
		P. Shanklin	& 37	& 0.756 \\
		I. Pyles	& 177	& 0.754 \\
		Gazebo		& 377	& 0.754 \\
		zimlord		& 217	& 0.747 \\
		C. Foy		& 205	& 0.739 \\
		B. Abear	& 29	& 0.733 \\
		Blazing		& 21	& 0.729 \\
		Mootz		& 29	& 0.715 \\
		Insane Steve	& 49	& 0.714 \\
	\end{tabular}
	\end{center}
	\caption{The turniest and least turny step authors. Only authors with 10 or more charts are included.}
	\label{tab:artist}
\end{table}
Beyond these extreme examples, we are interested in some more normal charts people might actually like to play.
Table~\ref{tab:feets} shows the turniest charts of each level, for the most popular difficulty levels ranging from 7 to 17.
So, next time you want to work on your laterals or candles, you have me to thank!

@@

\defcitealias{ode}{Anonymized 2016}
{\bf Jumps.} The most obvious next step for this work is to account for jumps.
This seems quite easy: compute the two possible facings of the jump, depending which foot lands on which arrow, and use whichever facing produces the least turniness when compared to the previous and next steps in the sequence.
Honestly, we should have implemented that for this paper, but we only realized how it should work after we finished computing our dataset;
and owing to an inferior conference's deadline coming up in 10 days, we don't have time for re-running experiments \citepalias{ode}.

@@

{\bf Fractional Turns.}
Experienced ITG players do not step with their feet on the middle of each arrow; rather, they try to step on the edges and ``brackets'' between arrows, hitting each step with heel or toes only to minimize the distance their feet must move.
This tendency distinguishes further granularity of turning than what we identify in this work.
Consider the two streams shown in Figure~\ref{fig:future} (a) and (b).
Although they measure the same $\mathcal{T}$ value of $1$,
(b) is considerably more exhausting to step, as (a) allows the player to bracket the entire run.
Future work could handle this by counting a 1-turn step as the full value only if the player subsequently continues turning farther in the same direction (which would force the player's feet off the brackets), and otherwise assign $0<\mathcal{T}<1$ for such a step.

@@

Following are the most turny 18-step patterns that are totally vanilla, with $\mathcal{T}=1.375$. (Manual inspection reveals the true turniness to be 4/3.)

@@

Following are the most turny 18-step patterns that may include crossovers only, with $\mathcal{T}=1.5$.

@@

Following are the most turny 18-step patterns that may include crossovers and laterals, with $\mathcal{T}=1.625$. (Manual inspection reveals the true turniness to be 8/5.)

@@

Following are the most turny 18-step patterns that may include crossovers, laterals, and 270s, with $\mathcal{T}=1.625$.
(Manual inspection reveals irregularity; these streams exhibit no core pattern that can be repeated to retain the maximum turniness.)

@@

Following are the most turny 18-step patterns that may include any pattern, with $\mathcal{T}=2$.

@@

\section{Related Work...?}

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=0.48\textwidth]{machine-translation.jpg}
	\end{center}
	\caption{We employ the techniques of \cite{deltax} for ITG machine translation.} %All photos credit \cite{alanv}.
	\label{fig:machine-translation}
\end{figure}
\bibliographystyle{abbrvnat}
\bibliography{citations}
